---
title: "SRT411assignment0"
author: "juan zhao"
date: "February 2, 2017"
output:
  pdf_document: default
  html_document: default
---


#3.1 ToDo:
Compute the difference between 2014 and the year  you  started  at  this  university  and  divide this by the difference between 2014 and the year you  were  born.   Multiply  this  with  100  to  get the  percentage  of  your  life  you  have  spent  at
this university.  Use brackets if you need them
```{r}
(2017-2014)/(2014-1985)*100
```
#3.2 TODO
Repeat  the  previous  ToDo,  but  with  several steps  in  between.   You  can  give  the  variables any name you want, but the name has to start with a letter.
```{r}
Cur_Year = 2017
My_Birth = 1985
(Cur_Year - 2014)/(2014 - My_Birth)*100
```
#3.4 TODO
Compute the sum of 4, 5, 8 and 11 by first com-bining  them  into  a  vector  and  then  using  the function sum
```{r}
a=c(4,5,8,11)
sum(x=a)
```
#3.5 TODO
Plot 100 normal random numbers.
```{r}
x = rnorm(100)
plot(x)
```
#4.0 TODO
Find help for the sqrt function.
```{r}
help(sqrt)
```
#6.0 TODO
Put  the  numbers  31  to  60  in  a  vector  named P and in a matrix with 6 rows and 5 columns named Q. Tip:  use the function
seq.  Look at the different ways scalars, vectors and matrices are denoted in the workspace window.
```{r}
P = seq(31,60)
Q = matrix(data=P, ncol=5,nrow=6)
P
Q
```
#5.0 TODO
Make a file called firstscript.R containing R- code  that  generates  100  random  numbers  and plots them, and run this script several times.
```{r}
earrings = 1
while (earrings < 6) {
  plot(rnorm(100))
  earrings = earrings+1
}

```

#6.3 TODO
Make  a  script  file  which  constructs  three  random  normal  vectors  of  length  100.   Call  these vectors x1,x2andx3. Make a data frame called t with three columns (called a,b and c) containing  respectively x1,x1+x2 and x1+x2+x3. Call the following functions for this data frame: plot(t) and sd(t).  Can you understand the results?  Rerun this script a few times
```{r}
x1 =c(rnorm(100))
x2 = c(rnorm(100))
x3 = c(rnorm(100))
t = data.frame(a=x1,b=x1+x2,c=x1+x2+x3 )
plot(t)

```
#7.0 TODO
Add these lines to the script file of the previous section.  Try to find out, either by experimenting or by using the help, what the meaning is of rgb, the last argument of rgb,lwd,pch,cex.
```{r}
plot(t$a, type="l", ylim=range(t),lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,col=rgb(0,0,1,0.3))
```


#8.0 TODO
Make  a  file  called tst1.txt in  Notepad  from the  example  in  Figure  4  and  store  it  in  your working directory.  Write a script to read it, to multiply the column called g by 5 and to store it as tst2.txt.
```{r}
D8= read.table(file = "/home/juan/SRT411/SRT411-Assignment-0/tst1.txt", header =TRUE)
write.table(D8$g*5, file=  "/home/juan/SRT411/SRT411-Assignment-0/tst1.txt",row.names=FALSE)
D8

```
#9.0 TODO
Compute the mean of the square root of a vector  of  100  random  numbers.   What  happens?
```{r}
##V9=c(rnorm(100), na.rm=TRUE)
V9=c(runif(n=100, min=0, max=100))
V9
j=c(1,2,NA)
max(j)
max(j,na.rm = TRUE)
max(V9, na.rm=TRUE)
mean(sqrt(V9), na.rm = TRUE)

```
#10.2 Dates 
Make  a  graph  with  on  the  x-axis:  today,  Sinterklaas  2014  and  your  next  birthday  and  on the y-axis the number of presents you expect on each of these days.  Tip:  make two vectors first
```{r}
date1=strptime(c("20170201","20171225","20170216"),format = "%Y%m%d")

d<- data.frame(date1=c("20170201","20171225","20170216"),presents=c("2","3","4"))
##d<- data.frame(date1,presents=c("2","3","4"))
x<-d$date1
y<-d$prensents

plot(x,y,xlab="date1",ylab="presents")
```
#11.2 TODO
Make a vector from 1 to 100.  Make a for-loop which runs through the whole vector.  Multiply the elements which are smaller than 5 and larger than 90 with 10 and the other elements with 0.1.
```{r}
s=c()
for(i in 1:100)
 {if (i<5 | i >90)
   {s[i]=i * 10
   }else{
   s[i]=i*0.1
   }
}
s
```
#11.3 TODO
Write  a  function  for  the  previous  ToDo,  so that   you   can   feed   it   any   vector   you   like (as  argument).Use  a  for-loop  in  the  function  to  do  the  computation  with  each  element.    Use  the  standard  R  function length in   the   specification   of   the   counter.
```{r}
fun1=function(arg1,arg2)
{
s=c()
for(i in arg1:arg2)
 {if (i<5 | i >90)
   {s[i]=i * 10
   }else{
   s[i]=i*0.1
   }
}
s
}
fun1(arg1=3,arg2=50)
```

